## Distance added to Random Forests (DistRF)

The R package `DistRF`The R package `DistRF` calculates euclidean distance as well as log-likelihood to
improve classification when handling imbalanced data. In addition, the package provides tools to evaluate
the performance of the classifier considering imbalanced data. The measures available are True positive rate,
True negative rate, Area under the curve and ROC curve.


`DistRF` can be loaded using the `library` command:
```{r, message=FALSE}
library(DistRF)
```


I simulated some data for a binary classification where `x1` is continuous and `x2` is categorical. 

```{r seed_random}
# set seed for random number generation
set.seed(1231)                           
```

```{r simulate_data}
  # simulate data for classification
  n <- 10000
  x1 <- rnorm(n, 0, 2)
  x2 <- rnorm(n,-2,2)

  e <- rnorm(n,sd = 2)
  y <- as.factor((x2-sin(3*x1)+2*x1-6+e)>0) 
  data <- data.frame(y,x1,x2=cut(x2,c(-Inf,-4,-2,0,Inf)))
  
  head(data)
```



###  A. Add euclidean distance
```{r dist}
data$dist <- DistRF::distance(data[,c("x1","x2")],data$y)
```


###  B. Add log-likelihood
```{r loglik}
data$loglik <- DistRF::est_likelihood(data[,c("x1","x2")],data$y)
```


### C. Evaluate performance of Random Forest with no additional topological information

```{r evaluate1}
mod1 <- randomForest::randomForest(y~x1+x2,data = data)
acc_meas(mod1$confusion[,1:2])
```

### Evaluate performance of Random Forest with euclidean distance 

```{r evaluate2}
mod2 <- randomForest::randomForest(y~x1+x2+dist,data = data)
acc_meas(mod2$confusion[,1:2])
```

### Evaluate performance of Random Forest with  log-likelihood

```{r evaluate3}
mod3 <- randomForest::randomForest(y~x1+x2+loglik,data = data)
acc_meas(mod3$confusion[,1:2])
```
